Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-04-17 ms.tex
I added some examples of different averaging methods for the reference stars.

>>>>

We considered several ways to do reference summation.
Under consideration were two choices:
\begin{itemize}
	\item How to weight the stars (by flux, equally, variance)?
	\item Which stars to include in the summation?
\end{itemize}
Figure \ref{fig:refSumMethods} shows these 4 combinations of these two choices.
Clearly reference star 2 adds noise to the time series, but this does not affect the total summation method since it has lower flux.
When normalizing each time series before summation, this appears to decrease the linear trend in the data.
In all cases, there is an apparent transit-like feature near JD = 2457551.82.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/reference_method.pdf}
\caption{Corrected time series for \shStar\ when using different combinations of averaging the reference stars: i) Summing all stars equally ii) Summing the best stars [1,3,4,5,6], iii) Summing the normalized time series of the best stars iv) summing the normalized time series of the best stars.}\label{fig:refSumMethods}
\end{centering}
\end{figure}
